---
title: "Swiss Fertility and Socioeconomic Indicators (1888)"
author: "Lars Mehwald and Daniel Salgado Moreno"
date: "2 October 2015"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### The Data

This data set contains 47 observations and 6 variables: 

1. Fertiliy
2. Agriculture
3. Examination 
4. Education
5. Catholic
6. Infant.Mortality

All variables are in percentage in a Range from [0; 100]  
  
  
### Correlation Matrix
```{r corrm, echo=FALSE}
data(swiss)
library(magrittr, dplyr)
cor(swiss) %>% symnum()
```
  
  As observed in the matrix, Education and Agriculture have a high negative correlation of around 0.6 points. 
  
### Distribution of Education attainment in Swiss Cantons (1888)  
```{r hist_edu, fig.height=4, fig.width=5,echo=FALSE}
data("swiss")
hist(swiss$Education, main = 'Swiss Canton Education Attainment (1888)',
      xlab='% education beyond primary school for draftees')
```
  
  
  We need to adjust the distribution for Education. This is done by using the natural logarithm of Education.  
  
```{r hist_logedu, fig.height=4, fig.width=5,echo=FALSE}
data(swiss)
library(magrittr, dplyr)
log(swiss$Education) %>% hist(main = "Swiss Education Adjusted", xlab='Ln education beyond primary school for draftees')
```
  
  Now the Agriculture frequency distribution.  
```{r hist_agr, fig.height=4, fig.width=5,echo=FALSE}
data("swiss")
hist(swiss$Agriculture, main = 'Swiss Canton Males in agriculture ocupation (1888)',
      xlab='% of males involved in agriculture as occupation')
```
  
  ----  
  
### Relation between natural logarithm of Education and Agricultrue ocupation  

```{r ggplot, fig.align='default',fig.height=4, fig.width=4, echo=FALSE}
data("swiss")
library(ggplot2)
ggplot2::ggplot(swiss, aes(log(Education), Agriculture)) +
  geom_point() + geom_smooth() + theme_bw()
```
  
  
As seen in the plot, the negative relation between percentage of population with education above primary and the percentage of the population ocupaided in the agriculture sector. 

